An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-17 paper.tex
6 -> 3

Trials 6--8 use an early experimental protocol which divided the walking period
into three sections: no perturbation, longitudinal perturbation, and a
combination of longitudinal and lateral perturbation. The calibration pose and
zeroing events are present in the data but lumped into one event. These trials
only use the lower body marker set described in Table~\ref{tab:marker-labels}.
Additionally, there are five markers that have labels beginning with \verb|ROT|
that were attached to the treadmill base to capture the lateral motion. Trials
9--15 use the final protocol but have corrupt ground reaction loads due to the
wooden treadmill base stabilizers.

>>>>

Trials 3--8 use an early experimental protocol which divided the walking period
into three sections: no perturbation, longitudinal perturbation, and a
combination of longitudinal and lateral perturbation. The calibration pose and
zeroing events are present in the data but lumped into one event. These trials
only use the lower body marker set described in Table~\ref{tab:marker-labels}.
Additionally, there are five markers that have labels beginning with \verb|ROT|
that were attached to the treadmill base to capture the lateral motion. Trials
9--15 use the final protocol but have corrupt ground reaction loads due to the
wooden treadmill base stabilizers.
